Paper Figures and Text

### 2022-12-01 Fish Data Analysis/Paper_Figures.qmd
Wrote code to swap IDs in the CSVs

dot_binwidth = 0.015
```

@@

```{r}
eight_fish_all_cond <- ggplot(turning_data_sum %>% filter(Type == "Eight Fish"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Flow))+
  geom_point()+
  geom_line(alpha = 0.25) +
  facet_wrap(~ Darkness + Ablation) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_colour_manual(values = c(light_ab_color,dark_no_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))

@@

eight_fish_still_model <- ggplot(annushka_turning_data %>% filter(Flow == "Still Water"),
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Flow_Ablation_Darkness))+
  #geom_jitter(alpha = 0.1, height = 0.025)+
  geom_line(aes(x = Fish_Num_Ratio, y = predict(only_still_model, type="response"), color = Flow_Ablation_Darkness)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predict(only_still_model, type="response"), color = Flow_Ablation_Darkness)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ggtitle("GLM Model of the Probability of a Right Turn in Still Water") +
   ylim(0,1) +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))

@@

eight_fish_flow_model <- ggplot(annushka_turning_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Flow_Ablation_Darkness))+
  #geom_jitter(alpha = 0.1, height = 0.025)+
  geom_line(aes(x = Fish_Num_Ratio, y = predict(only_flow_model, type="response"), color = Flow_Ablation_Darkness)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predict(only_flow_model, type="response"), color = Flow_Ablation_Darkness)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  ggtitle("GLM Model of the Probability of a Right Turn in Flowing Water (2 BL/s)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))

@@

dark_eight_and_single_graph <- ggplot(all_turning_data %>% filter(Flow == "Still Water" & Darkness == "Dark"),
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Type))+
  geom_line(aes(x = Fish_Num_Ratio, y = predict(dark_eight_and_single_model, type="response"), color = Type)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predict(dark_eight_and_single_model, type="response"), color = Type)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  ggtitle("GLM Model of the Probability of a Right Turn Darkness for Eight or Single Fish") +
  scale_colour_manual(values = c(sim_color,dark_no_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))

@@

ablation_eight_and_single_graph <- ggplot(all_turning_data %>% filter(Flow == "Still Water" & Ablation == "Ablated"),
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Type))+
  geom_line(aes(x = Fish_Num_Ratio, y = predict(ablation_eight_and_single_model, type="response"), color = Type)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predict(ablation_eight_and_single_model, type="response"), color = Type)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  ggtitle("GLM Model of the Probability of a Right Turn Ablated for Eight or Single Fish") +
  scale_colour_manual(values = c(sim_color,light_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))

@@

light_eight_and_single_graph <- ggplot(all_turning_data %>% filter(Flow == "Still Water" & Ablation == "No Ablation" & Darkness == "Light"),
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Type))+
  geom_line(aes(x = Fish_Num_Ratio, y = predict(light_eight_and_single_model, type="response"), color = Type)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predict(light_eight_and_single_model, type="response"), color = Type)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  ggtitle("GLM Model of the Probability of a Right Turn Light for Eight or Single Fish") +
  scale_colour_manual(values = c(sim_color,light_no_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))

@@

nnd_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE)

nnd_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Flow (2 BL/s)") +
  xlab("") +
  ylab("NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE)

@@

my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))

polar_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Polar,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Polar_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Polar_Mean_Val-Polar_SD_Val, ymax=Polar_Mean_Val+Polar_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  ggtitle("Effect of Available Senses on Polarization in Still Water") +
  xlab("") +
  ylab("Polarization") +
  theme_light()+ 
  theme(legend.position = "none") +
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE)

polar_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Polar,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Polar_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Polar_Mean_Val-Polar_SD_Val, ymax=Polar_Mean_Val+Polar_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  ggtitle("Effect of Available Senses on Polarization in Flowing Water (2 BL/s)") +
  xlab("") +
  ylab("Polarization") +
  theme_light()+ 
  theme(legend.position = "none") +
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE)

@@

speed_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Speed,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Speed_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Speed_Mean_Val-Speed_SD_Val, ymax=Speed_Mean_Val+Speed_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
  xlab("") +
  ylab("Speed (BL/s)") +
  theme_light()+ 
  theme(legend.position = "none") +
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE)

speed_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Speed,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Speed_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Speed_Mean_Val-Speed_SD_Val, ymax=Speed_Mean_Val+Speed_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  ggtitle("Effect of Available Senses on Speed (BL/s) in Flowing Water (2 BL/s)") +
  xlab("") +
  ylab("Speed (BL/s)") +
  theme_light()+ 
  theme(legend.position = "none") +
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE)

>>>>

dot_binwidth = 0.0125
```

@@

```{r}
eight_fish_all_cond <- ggplot(turning_data_sum %>% filter(Type == "Eight Fish"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Flow))+
  geom_point()+
  geom_line(alpha = 0.25) +
  facet_wrap(~ Darkness + Ablation) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_colour_manual(values = c(light_ab_color,dark_no_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))

@@

eight_fish_still_model <- ggplot(annushka_turning_data %>% filter(Flow == "Still Water"),
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Flow_Ablation_Darkness))+
  #geom_jitter(alpha = 0.1, height = 0.025)+
  geom_line(aes(x = Fish_Num_Ratio, y = predict(only_still_model, type="response"), color = Flow_Ablation_Darkness)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predict(only_still_model, type="response"), color = Flow_Ablation_Darkness)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  #ggtitle("GLM Model of the Probability of a Right Turn in Still Water") +
   ylim(0,1) +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory Conditions")

@@

eight_fish_flow_model <- ggplot(annushka_turning_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Flow_Ablation_Darkness))+
  #geom_jitter(alpha = 0.1, height = 0.025)+
  geom_line(aes(x = Fish_Num_Ratio, y = predict(only_flow_model, type="response"), color = Flow_Ablation_Darkness)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predict(only_flow_model, type="response"), color = Flow_Ablation_Darkness)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  #ggtitle("GLM Model of the Probability of a Right Turn in Flowing Water (2 BL/s)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory Conditions")

@@

dark_eight_and_single_sum <- all_turning_data %>% filter(Flow == "Still Water" & Darkness == "Dark") %>%
                                                  mutate(predicted = predict(dark_eight_and_single_model, type="response")) %>%
                                                  group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
                                                  summarise(predicted = predicted, n = n()) %>%
                                                  ungroup()

dark_eight_and_single_graph <- ggplot(dark_eight_and_single_sum,
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Type))+
  geom_line(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predicted, color = Type, size = n)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  #ggtitle("GLM Model of the Probability of a Right Turn Darkness for Eight or Single Fish") +
  scale_colour_manual(values = c(sim_color,dark_no_ab_color)) +
  scale_size_continuous(breaks = c(25,50,75)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7")) + 
  labs(size = "Number of Turns")

@@

ablation_eight_and_single_sum <- all_turning_data %>% filter(Flow == "Still Water" & Ablation == "Ablated")  %>%
                                                  mutate(predicted = predict(ablation_eight_and_single_model, type="response")) %>%
                                                  group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
                                                  summarise(predicted = predicted, n = n()) %>%
                                                  ungroup()

ablation_eight_and_single_graph <- ggplot(ablation_eight_and_single_sum,
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Type))+
  geom_line(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predicted, color = Type, size = n)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  #ggtitle("GLM Model of the Probability of a Right Turn Ablated for Eight or Single Fish") +
  scale_colour_manual(values = c(sim_color,light_ab_color)) +
  scale_size_continuous(breaks = c(25,50,75)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(size = "Number of Turns")

@@

light_eight_and_single_sum <- all_turning_data %>% filter(Flow == "Still Water" & Ablation == "No Ablation" & Darkness == "Light")  %>%
                                                  mutate(predicted = predict(light_eight_and_single_model, type="response")) %>%
                                                  group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
                                                  summarise(predicted = predicted, n = n()) %>%
                                                  ungroup()

light_eight_and_single_graph <- ggplot(light_eight_and_single_sum,
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Type))+
  geom_line(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predicted, color = Type, size = n)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  #ggtitle("GLM Model of the Probability of a Right Turn Light for Eight or Single Fish") +
  scale_colour_manual(values = c(sim_color,light_no_ab_color)) +
  scale_size_continuous(breaks = c(25,50,75)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(size = "Number of Turns")

@@

```{r}
my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))

nnd_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,3)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))

nnd_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Flow (2 BL/s)") +
  xlab("") +
  ylab("NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,3)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

@@

my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))
polar_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Polar,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Polar_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Polar_Mean_Val-Polar_SD_Val, ymax=Polar_Mean_Val+Polar_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Polarization in Still Water") +
  xlab("") +
  ylab("Polarization") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,1.15)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))

polar_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Polar,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Polar_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Polar_Mean_Val-Polar_SD_Val, ymax=Polar_Mean_Val+Polar_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Polarization in Flowing Water (2 BL/s)") +
  xlab("") +
  ylab("Polarization") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,1.15)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

@@

speed_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Speed,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Speed_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Speed_Mean_Val-Speed_SD_Val, ymax=Speed_Mean_Val+Speed_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
  xlab("") +
  ylab("Speed (BL/s)") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,8.5)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))

speed_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Speed,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Speed_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Speed_Mean_Val-Speed_SD_Val, ymax=Speed_Mean_Val+Speed_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Speed (BL/s) in Flowing Water (2 BL/s)") +
  xlab("") +
  ylab("Speed (BL/s)") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,8.5)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))
